### 2023-12-01 manuscript.tex
Removed superfluous use of observed to refer to data
Expanded some discussion in final discussion section

\subsection{Future evolutionary analyses of IDRs will require a multimodal approach}
As discussed by Zarin \textit{et al.}, the interpretation of evolutionary signatures is complicated by several methodological limitations~\cite{Zarin2019}. For example, because IDRs are identified as contiguous segments of high predicted disorder, their boundaries are defined by adjacent structural elements. This approach can therefore split an IDR that is a single evolutionary or functional unit if it contains a semi-disordered module that scores below the threshold. Conversely, it can also merge two distinct IDRs if they are not separated by at least one folded domain.

% TODO: Expand with more discussion for consequences of ``fuzzy'' boundaries on feature calculations
% Inclusion regions in alignments can create signals of conserved features
% Not incorrect, but not a biologically interesting insight
% More targeted applications of this framework where investigators choose boundaries of interest for specific IDRs or exclude conserved sub-regions can ensure the results are directly related to the rapidly evolving regions of IDRs.

Another challenge is the significant overlap in the definitions of many features induces strong correlations that preclude straightforward quantitative manipulations or interpretations of an IDR's evolutionary signature. The original authors have since addressed this in subsequent studies by applying machine learning methods to perform feature selection or learn features directly from alignments of IDRs~\cite{Zarin2021, Lu2022}. However, integrating these methods into a unified phylogenetic comparative framework will require further effort.

% TODO: Add note about annotations not at level of regions
% That proteins are annotated at the level of entire sequences further compounds these issues, as it is unclear that if annotations are specifically associated with the IDRs in the identified clusters.

By fitting the BM and OU models to molecular features calculated from alignments of IDRs, we were able to quantify the relative support for constrained and unconstrained models of IDR evolution using a statistical framework. As the BM and OU models describe the evolution of arbitrary continuous traits, a strength of this approach is its independence from assumptions about the underlying process of sequence evolution. In contrast, the previous study used simulations to generate null distributions for a model of no constraint and defined an IDR's evolutionary signature as its deviation from these distributions. However, these comparisons do not directly demonstrate evidence of stabilizing selection but instead test for differences from the null hypothesis. Thus, this approach is highly dependent on the specification and parameterization of these simulated models. Accordingly, an error in either can yield evidence of constraint for an IDR even if none of its molecular features are under selection.

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{conserved/out/conserved.png}
\centering
\caption{\textbf{Distributions of significant features in regions.}
\textbf{(A)} Fraction of regions with significant likelihood ratios for each feature under 1 and 5\% type I error rates.
\textbf{(B)} Distribution of number of features with significant likelihood ratios under 1 (left) and 5\% type I error rates. The random distributions were computed by randomly shuffling the observed likelihood ratios between regions for each feature independently.}
\label{fig:conserved}
\end{figure}

>>>>

\subsection{Future evolutionary analyses of IDRs will require a multimodal approach}
As discussed by Zarin \textit{et al.}, the interpretation of evolutionary signatures is complicated by several methodological limitations~\cite{Zarin2019}. For example, because IDRs are identified as contiguous segments of high predicted disorder, their boundaries are defined by adjacent structural elements. This approach can therefore split an IDR that is a single evolutionary or functional unit if it contains a semi-disordered module that scores below the threshold. Conversely, it can also merge two distinct IDRs if they are not separated by at least one folded domain. These issues can have significant effects on the accuracy of our statistical analysis, as mismatches between the inferred boundaries of an IDR and its true evolutionary or functional divisions can introduce noise or even spurious signals of constraint. However, more targeted applications of this framework where investigators manually choose the boundaries for specific IDRs can ensure the results are directly related to the regions of interest.

Another challenge is the significant overlap in the definitions of the features used in this study. As a result, many are highly correlated, which precludes straightforward quantitative manipulations or interpretations of an IDR's evolutionary signature. Additionally, the features were originally compiled from a variety of previous reports on IDRs. Thus, they likely reflect the biases of individual investigators or highly studied examples rather than constituting a comprehensive set of IDR-associated properties. The original authors have since addressed this in subsequent studies by applying machine learning methods to perform feature selection or learn features directly from alignments of IDRs~\cite{Zarin2021, Lu2022}. However, integrating these methods into a unified phylogenetic comparative framework will require further effort.

Despite these caveats, by fitting the BM and OU models to molecular features calculated from alignments of IDRs, we were able to quantify the relative support for constrained and unconstrained models of IDR evolution using a statistical framework. As the BM and OU models describe the evolution of arbitrary continuous traits, a strength of this approach is its independence from assumptions about the underlying process of sequence evolution. In contrast, the previous study used simulations to generate null distributions for a model of no constraint and defined an IDR's evolutionary signature as its deviation from these distributions. However, these comparisons do not directly demonstrate evidence of stabilizing selection but instead test for differences from the null hypothesis. Thus, this approach is highly dependent on the specification and parameterization of these simulated models. Accordingly, an error in either can yield evidence of constraint for an IDR even if none of its molecular features are under selection.

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{conserved/out/conserved.png}
\centering
\caption{\textbf{Distributions of significant features in regions.}
\textbf{(A)} Fraction of regions with significant likelihood ratios for each feature under 1 and 5\% type I error rates.
\textbf{(B)} Distribution of number of features with significant likelihood ratios under 1 (left) and 5\% type I error rates. The random distributions were computed by randomly shuffling the likelihood ratios between regions for each feature independently.}
\label{fig:conserved}
\end{figure}
